---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# summclust

<!-- badges: start -->
[![R-CMD-check](https://github.com/s3alfisc/summclust/workflows/R-CMD-check/badge.svg)](https://github.com/s3alfisc/summclust/actions)
<!-- badges: end -->

R module for cluster level measures of leverage and influence.

For a very detailed description see:

[MacKinnon, J.G., Nielsen, M.Ø., Webb, M.D., 2022. Leverage, influence, and the jackknife in clustered regression models: Reliable inference using summclust](https://arxiv.org/abs/2205.03288). QED Working Paper 1483. Queen’s University.

A standalone R implementation of the cluster jackknife estimator discussed in MNW is implemented in the [CRV3J package](https://github.com/s3alfisc/CRV3J).

## Installation

You can install the development version of summclust from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("s3alfisc/summclust")
```

## Example


```{r example, warning = FALSE, message = FALSE, out.width="50%", out.height="50%"}
library(summclust)
library(lmtest)
library(haven)

nlswork <- read_dta("http://www.stata-press.com/data/r9/nlswork.dta")
# drop NAs at the moment
nlswork <- nlswork[, c("ln_wage", "grade", "age", "birth_yr", "union", "race", "msp", "ind_code")]
nlswork <- na.omit(nlswork)

lm_fit <- lm(
  ln_wage ~ as.factor(grade) + as.factor(age) + as.factor(birth_yr) + union +  race + msp,
  data = nlswork)

summclust_res <- summclust(
  obj = lm_fit,
  cluster = ~ind_code,
  type = "CRV3")

# CRV3-based inference - exactly matches output of summclust-stata
coeftable(summclust_res, param = "msp")
coeftable(summclust_res, param = "union")

summary(summclust_res, param = "msp")
```

To plot the leverage statistics, use the `plot` method

```{r, warning = FALSE, message = FALSE, out.width="50%"}
plot(summclust_res, param = c("msp","union"))
```


Note that you can also use CVR3 and CRV3J covariance matrices computed via `summclust` with the `lmtest()` and `fixest` packages.

```{r, warning = FALSE, message=FALSE}
library(lmtest)
library(fixest)

df <- length(summclust_res$cluster) - 1

# with lmtest
CRV1 <- coeftest(lm_fit, sandwich::vcovCL(lm_fit, ~ind_code), df = df)
CRV3 <- coeftest(lm_fit, summclust_res$vcov, df = df)

CRV1[c("union", "race", "msp"),]
CRV3[c("union", "race", "msp"),]

confint(CRV1)[c("union", "race", "msp"),]
confint(CRV3)[c("union", "race", "msp"),]

# with fixest
feols_fit <- feols(
  ln_wage ~ as.factor(grade) + as.factor(age) + as.factor(birth_yr) + union +  race + msp,
  data = nlswork)

fixest::coeftable(
  feols_fit,
  vcov = summclust_res$vcov,
  ssc = ssc(adj = FALSE, cluster.adj = FALSE)
)[c("msp", "union", "race"),]

```

Note that the p-value and confidence intervals for `fixest::coeftable()` differs from `lmtest::coeftest()` and `summclust::coeftable()`. This is due to a fact that `fixest::coeftable()` uses a different degree of freedom for the t-distribution used in these calculation (I believe it uses t(N-1)).

